Efficient spherical Convolutional Neural Networks with Healpix sampling for cosmological applications

### 2018-05-01 scnn.tex
update convolution

\subsection{Graph Fourier basis and spherical harmonics}

@@

\subsection{Convolutions on graphs}
\assign{Nathanaël, Michaël}

@@

\paragraph{Example: heat diffusion}
Let us consider the heat diffusion problem 
\begin{equation} \label{eq:heat_equation}
\L \b{f}(t) = \tau \partial_t \b{f}(t),
\end{equation}
where $\b{f}(t): \mathbb{R}_+ \rightarrow \mathbb{R}^N$. Given the initial condition 
$\b{f}(0)$, the solution of~\ref{eq:heat_equation} can be expressed as
\begin{equation}
\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U^* \g{f}(0) = K_t(\L) \b{f}(0), 
\end{equation}
which is a convolution of the signal $\b{f}(0)$ with the kernel 
$K_t(x)=e^{-\tau t x}$. Here the kernel $K_t$ is applied to the correspond
In Figure~\ref{fig:gaussian_filters_comparizon}, we show the effect of the convolution by diffusing a unit of heat for various amount of time.

Example on the heat equation
\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_sphere.pdf}
\caption{Top: Diffusion of a unit of heat for different time using the graph. Bottom: gaussian filtering on the sphere. Relative difference of the two diffusions: $13.5$\%, $6.1$\%, $5.2$\%, $3.8$\% }
\label{fig:gaussian_filters_comparizon}
\end{figure}

Figure filters 3 representations for both graph + spherical Fourier
\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_spectral.pdf}
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_gnomonic.pdf}
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_section.pdf}
\caption{3 Different effet visualization of filters. Top: Graph spectral domain. Middle: gnomonic projection on the sphere. Bottom: section of filter.}
\label{fig:gaussian_filters_visualization}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/index_plotting_order20_nside16.pdf}
\caption{Indexes selected for the section ploting of the filter.}
\label{fig:index_section}
\end{figure}

@@

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
%% \appendix

%% \section{}
%% \label{}

>>>>

\subsection{Graph Fourier basis and spherical harmonics}
\todo{Add a few extra references}

@@

\subsection{Convolutions on graphs}
\assign{Nathanaël, Michaël} \todo{Add a few extra references}

@@

\paragraph{Example: heat diffusion}
Let us consider the heat diffusion problem 
\begin{equation} \label{eq:heat_equation}
\L \b{f}(t) = \tau \partial_t \b{f}(t),
\end{equation}
where $\b{f}(t): \mathbb{R}_+ \rightarrow \mathbb{R}^N$. Given the initial condition 
$\b{f}(0)$, the solution of~\ref{eq:heat_equation} can be expressed as
\begin{equation}
\b{f}(t) = e^{-\L \tau t} \b{f}(0) = \U e^{-\bLambda t \tau} \U^* \g{f}(0) = K_t(\L) \b{f}(0), 
\end{equation}
which is a convolution of the signal $\b{f}(0)$ with the kernel $K_t(x)=e^{-\tau
t x}$. Here the kernel $K_t$ is applied to the graph eigenvalues $\bLambda$ that
correspond to the squared frequencies and hence $K_t$ can be considered a
Gaussian kernel. In Figure~\ref{fig:gaussian_filters_comparizon} top, we show
the effect of the convolution by diffusing a unit of heat for $\tau=1$ and various 
time $t$. In  Figure~\ref{fig:gaussian_filters_visualization} of
Appendix~\ref{app:filter_visualization}, we show different visualizaton of the
convolution kernel $K_t$. We also compare the graph convolution with the
spherical symmetric Gaussian smoothing
(Figure~\ref{fig:gaussian_filters_comparizon} bottom) and observe that both
techniques lead to similar results. While the graph convolution is different
from a true spherical convolution, it can, providing the correct
parametrization, well approximate it.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_sphere.pdf}
\caption{Convolution comparizon (Nside=16). 
Top: Diffusion of a unit of heat for different time $t$ using the graph. 
Bottom: spherical symmetric Gaussian smoothing for different $\sigma$ (arcmin). 
Relative difference between graph convolution and spherical smoothing: $10.4$\%, $5.7$\%, $4.8$\%, $3.8$\% }
\label{fig:gaussian_filters_comparizon}
\end{figure}

It is another sign that the constructed graph is able to capture the spherical
structure of the healpix sampling. Furthemore, in some application, where the
exactitude of the convolution is not requirement, such as de-noising, it means
that we could use graph convolution instead. Depending on the convolution kernel
this may reveal much more efficient. In the case of a neural network, the fact
that both convolution are not identical is not very relevant since the network
will adapt the convolution at use.

@@

%% The Appendices part is started with the command \appendix;
%% appendix sections are then done as normal sections
\appendix

\section{Filter visualization}
\label{app:filter_visualization}

In Figure~\ref{fig:gaussian_filters_visualization}, we present three different
ways to plot the graph convolution kernel $K_t(x)=e^{-\tau t x}$.  First, it can
be ploted in the graph spectral domain. In this case, we simply evaluate $K_t$
at the graph eigenvalues $\text{diag}(\bLambda)$. Second, we can convolve a
delta on the sphere and plot a gnomonic view of the results. Third, since we are
working on the sphere, we can only plot the section of the convoluted delta. In
Figure~\ref{fig:index_section}, we display the selected indexes for the section
plotting. Note that, because of the small irregularities in the HealPix
sampling, the second and the third methods are likely to change depending on the
chosen delta.

\begin{figure}[!ht]
\centering
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_spectral.pdf}
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_gnomonic.pdf}
\includegraphics[width=0.95\textwidth]{figures/gaussian_filters_section.pdf}
\caption{3 different visualizations of the convolution kernel $K_t(x)=e^{-\tau t x}$.  
Top: graph spectral domain. 
Middle: gnomonic projection.
Bottom: section plot.}
\label{fig:gaussian_filters_visualization}
\end{figure}

\begin{figure}[!ht]
\centering
\includegraphics[width=0.45\textwidth]{figures/index_plotting_order20_nside16.pdf}
\caption{Indexes selected for the section ploting of Figure~\ref{fig:gaussian_filters_visualization} middle. The delta was placed on the yellow node.}
\label{fig:index_section}
\end{figure}
